Predicting complex diseases: performance and robustness [OF NEW METHOD?]

### 2018-03-08 5-results-celiac.Rmd
multiple runs

## Methods' functions

@@

```{r}
res.PRS <- PRS(
  G = G,
  infos.chr = CHR,
  infos.pos = POS,
  pheno.all = y,
  covar.all = obj.svd$u,
  ind.train = ind.train,
  ind.test = ind.test
)
# GWAS
system.time(
  gwas.train <- big_univLogReg(
    G, y[ind.train], ind.train = ind.train, 
    covar.train = obj.svd$u[ind.train, , drop = FALSE], 
    ncores = NCORES
  )
)
```

@@

```{r}
# Divide in training/test sets
ind.train <- sort(sample(nrow(G), size = 12e3))
ind.test <- setdiff(rows_along(G), ind.train)
```

```{r}
# PRS
PRS <- function() {

  system.time(
  gwas.train <- big_univLogReg(
    G, y[ind.train], ind.train = ind.train, 
    covar.train = obj.svd$u[ind.train, , drop = FALSE], 
    ncores = NCORES
  )
)
}

```

@@

>>>>

@@

```{r}
# GWAS
system.time(
  gwas.train <- big_univLogReg(
    G, y[ind.train], ind.train = ind.train, 
    covar.train = obj.svd$u[ind.train, , drop = FALSE], 
    ncores = NCORES
  )
)
```

@@

@@

### Methods' functions

#### PRS

#### Logistic regression

### Run multiple times

```{r, eval=TRUE}
if (!dir.exists("results6")) dir.create("results6")
pheno.all <- y
covar.all <- obj.svd$u

for (i in 1:100) {

  res.file <- paste0("results6/simu_", i, ".rds")
  if (file.exists(res.file)) next

  # Split in training/test sets
  ind.train <- sort(sample(nrow(G), size = 12e3))
  ind.test <- setdiff(rows_along(G), ind.train)

  # Get results from all methods
  res <- bind_rows(
    PRS(G, CHR, POS, pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G,  pheno.all, covar.all, ind.train, ind.test, "logit-simple"),
    logit.CMSA(G2, pheno.all, covar.all, ind.train, ind.test, "logit-triple")
  )
  saveRDS(res, file = res.file)
}
```
```{r}
pAUC <- function(pred, target, p = 0.1) {
  val.min <- min(target)
  q <- quantile(pred[target == val.min], probs = 1 - p)
  ind <- (target != val.min) | (pred > q)
  tryCatch(bigstatsr::AUC(pred[ind], target[ind]) * p, 
           error = function(e) p^2 / 2)  # all same prediction
}

format_results <- function(results) {
  results %>%
    as_tibble() %>%
    mutate(
      AUC = map_dbl(eval, ~ bigstatsr::AUC(.x[, 1], .x[, 2])),
      pAUC = map_dbl(eval, ~ pAUC(.x[, 1], .x[, 2]))
    )
}

boot <- function(x, n = 1e5, f = mean) {
  sd(replicate(n, f(sample(x, replace = TRUE))))
}

list.files(path = "results6/", full.names = TRUE) %>%
  map_df(readRDS) %>%
  format_results() %>%
  group_by(method) %>%
  summarize_at(-1, function(x) {
    glue::glue("{signif(mean(x), 3)} ({signif(boot(x), 3)})")
  }) %>%
  print() %>%
  xtable::xtable()
```

### 2018-03-08 paper/draft.tex
multiple runs

\begin{table}[h]
\caption{Results for the real Celiac dataset.\label{tab:results-celiac}}
\vspace*{0.5em}
\centering
\begin{tabular}{|l|c|c|c|c|}
\hline
Method & AUC (\%) & pAUC & \# predictors & Execution time (s) \\ \hline
PRS-max & 82.46 & 0.0283 & 13277 & 149 \\ 
logit-simple & 88.71 & 0.0411 & 2198 & 78 \\
logit-triple & 89.26 & 0.0440 & 4617 & 161 \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h]
\caption{Results for the real Celiac dataset. The results are averaged over 100 runs where the training step is randomly composed of 12,000 individuals. In the parentheses is reported the standard deviation of $10^5$ bootstrap samples of the mean of the corresponding variable. Results are reported with 3 significant digits.\label{tab:results-celiac}}
\vspace*{0.5em}
\centering
\begin{tabular}{|l|c|c|c|c|}
  \hline
Method & AUC & pAUC & \# predictors & Execution time (s) \\ 
  \hline
PRS-max & 0.824 (0.000704) & 0.0286 (0.00016) & 9850 (781) & 148 (0.414) \\ 
logit-simple & 0.888 (0.000468) & 0.0414 (0.000164) & 3220 (62) & 83.8 (1.27) \\ 
logit-triple & 0.892 (0.000488) & 0.0429 (0.000174) & 4470 (80.6) & 141 (1.85) \\ 
   \hline
\end{tabular}
\end{table}
